---
title: "ggplot_hook"
author: "Maj"
date: "2023-07-15"
output:
  html_document: default
  pdf_document: default
---

## Setting up my environment
Notes: setting up my R environment by loading the 'tidyverse' and  'palmer penguins' packages

```{r loading packages}
library(tidyverse)
library(palmerpenguins)
```

## Visualizations
Here we will go through a series of visualizations

### Flipper and body mass in purple
Here, we plot flipper length against body mass
```{r}
ggplot(data=penguins,aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(color="purple")

```

### Flipper and body mass by species
Here, we plot flipper length against body mass and look at the breakdown by species
```{r}
ggplot(data=penguins,aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(aes(shape=species))
```

### Flipper and body mass by species and sex
Here, we plot flipper length against body mass and look at the breakdown by species and sex

```{r}
ggplot(data=penguins,aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(aes(color=species,
                 shape=species)) +
  facet_wrap(~sex)
```

